Class Exercise: Factors Influencing Abundance & Virus Isolation in Mosquitoes

### 2024-02-02 products/manuscript/Manuscript.qmd
final push

head(mos_data)
summary(mos_data)

@@

```{r}
dp2 = here("data", "raw-data", "weather_airport.csv")
weather = read.csv(dp2, fileEncoding = "UTF-8")
head(weather)
summary(weather)
```

>>>>

head(mos_data)

@@

```{r}
dp2 = here("data", "raw-data", "weather_airport.csv")
weather = read.csv(dp2, fileEncoding = "UTF-8")
head(weather)
```
